Meta-Analysis of Variation in Sport and Exercise Science

### 2022-10-26 paper/Paper - Meta-Analysis of Variation in Sport and Exercise Science - anonymous.Rmd
Add anonymous version for submission

---
title: "Meta-Analysis of Variation in Sport and Exercise Science"
subtitle: "Examples of Application Within Resistance Training Research"
author: 
  - James Steele$^a$
  - James Fisher$^a$
  - Dave Smith$^b$
  - Brad Schoenfeld$^c$
  - Yefeng Yang$^d$
  - Shinichi Nakagawa$^d$
date: "18th October 2022"
abstract: "Meta-analysis has become commonplace within sport and exercise science for synthesising and summarising empirical studies. However, most research in the field focuses upon mean effects; particularly the effects of interventions to improve outcomes such as fitness or performance. It is well known that there is considerable variability in response to interventions. Hence, interest has increased in exploring *precision* or *personalised* exercise approaches. Not only is the mean often affected by interventions, but variances may also be impacted. Exploration of variances in studies such as randomised controlled trials (RCTs) can yield insight into the existence of interindividual heterogeneity in response to interventions and help determine the degree of generalisability of effects. Yet, larger samples sizes than those used for typical mean effects are required when probing variances. Thus, for a field with small samples such as sport and exercise science, exploration of variance through a meta-analytic framework is appealing. Given the value of embracing and exploring variation alongside mean effects in sport and exercise science, yet its lack of application in research synthesis by way of meta-analysis, we introduce and discuss effect size approaches and models for meta-analysis of variation using relatable examples from resistance training RCTs."
thanks: |
  Preprint, please cite as: Steele, J., Fisher, J., Smith, D., Schoenfeld, B., Yang, R., & Nakagawa, S. (2022). Meta-Analysis of Variation in Sport and Exercise Science: Examples of Application Within Resistance Training Research. $\textrm{sportr}\chi\textrm{iv}$ DOI: ????. 
  Address for correspondence: james.steele@solent.ac.uk
  Affiliations:
  $^a$Faculty of Sport, Health, and Social Sciences, Solent University, UK;
  $^b$Research Centre for Musculoskeletal and Sports Medicine, Manchester Metropolitan University, Manchester, UK;
  $^c$Health Sciences Department, CUNY Lehman College, Bronx, New York, USA;
  $^d$Evolution & Ecology Research Centre and School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, New South Wales, Australia
output: bookdown::pdf_document2
bibliography: references.bib
csl: apa.csl
toc: false
header-includes:
   - \usepackage{caption}
   - \captionsetup[figure]{font=small}
---

>>>>

---
title: "Meta-Analysis of Variation in Sport and Exercise Science"
subtitle: "Examples of Application Within Resistance Training Research"
date: "18th October 2022"
abstract: "Meta-analysis has become commonplace within sport and exercise science for synthesising and summarising empirical studies. However, most research in the field focuses upon mean effects; particularly the effects of interventions to improve outcomes such as fitness or performance. It is well known that there is considerable variability in response to interventions. Hence, interest has increased in exploring *precision* or *personalised* exercise approaches. Not only is the mean often affected by interventions, but variances may also be impacted. Exploration of variances in studies such as randomised controlled trials (RCTs) can yield insight into the existence of interindividual heterogeneity in response to interventions and help determine the degree of generalisability of effects. Yet, larger samples sizes than those used for typical mean effects are required when probing variances. Thus, for a field with small samples such as sport and exercise science, exploration of variance through a meta-analytic framework is appealing. Given the value of embracing and exploring variation alongside mean effects in sport and exercise science, yet its lack of application in research synthesis by way of meta-analysis, we introduce and discuss effect size approaches and models for meta-analysis of variation using relatable examples from resistance training RCTs."

output: bookdown::pdf_document2
bibliography: references.bib
csl: apa.csl
toc: false
header-includes:
   - \usepackage{caption}
   - \captionsetup[figure]{font=small}
---
